%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{center}
    {\Huge \scshape Yash Shukla} \\ \vspace{1pt}
    Jankinagar, Gonda, Uttar Pradesh 271001\\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 9838576734 ~
   \href{mailto:shuklayash457@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \textunderline{shuklayash457@gmail.com}}
  ~ 
    \href{https://www.linkedin.com/in/yash-shukla-b92553212/}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}}  ~
    \href{https://github.com/yashshuklaaa}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}}
    \vspace{-8pt}
\end{center}

%-----------PROFESSIONAL SUMMARY-----------
\section{Professional Summary}
\small{Full Stack \& AI Developer with over 3.5 years of experience engineering high-performance, scalable web solutions. Specialized in crafting robust backends and stunning user interfaces using the MERN stack and Next.js/React. Highly experienced in integrating AI-powered features, LLMs, and data extraction pipelines to build intelligent applications. Currently exploring Google Cloud Platform (GCP) and Vertex AI to drive next-generation, cloud-native machine learning solutions. Passionate about leveraging AI to automate complex processes and elevate user experiences.}
\vspace{2pt}

%-----------LIVE PROJECTS-----------
\section{Live Projects}
\vspace{4pt}

\textbf{MOOC Ed-Tech Platform (Jalshaala)} \\
\vspace{2pt}
\resumeItemListStart
\resumeItem{Developed a full-scale \textbf{Ed-Tech platform} from scratch, handling frontend, backend, authentication, database design, and deployment.}
\resumeItem{Implemented scalable architecture and interactive learning features for seamless user experience.}
\resumeItem{Live Link: \href{https://new.jalshaala.com/?showWebsite=true}{https://new.jalshaala.com/?showWebsite=true}}
\resumeItemListEnd

\vspace{6pt}

\textbf{ScalePart (eVehicle Platform)} \\
\vspace{2pt}
\resumeItemListStart
    \resumeItem{Built and contributed to an \textbf{eVehicle platform} focused on scalable solutions and modern UI/UX.}
    \resumeItem{Engineered a seamless \textbf{AI-driven data extraction pipeline} to parse complex PDFs into structured database records.}
    \vspace{-4pt}
    \resumeItem{Live Link: \href{https://scalepart.com/}{https://scalepart.com/}}
\resumeItemListEnd

\vspace{10pt}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

\resumeSubheading
{Troology}{Sept 2025 -- Present}
{Full Stack AI Developer}{On-Site}
\resumeItemListStart

\resumeItem{Currently spearheading the \textbf{eVehicle platform (ScalePart)}, developing both frontend architectures and backend AI integrations to handle unstructured catalog data.}
\resumeItem{Engineered an \textbf{AI-driven document extraction pipeline} utilizing external LLM endpoints to automatically parse complex PDF manuals and unstructured text, extracting precise product model numbers, series names, and technical specifications.}
\resumeItem{Built an \textbf{intelligent caching and confidence scoring layer} for AI responses, significantly reducing external API latency and costs while ensuring highly accurate data mapping to MongoDB schemas.}
\resumeItem{Contributed to the \textbf{UPSDMA (Uttar Pradesh State Disaster Management Authority)} platform (Rahat Sewa App) for SDRF personnel, building features ensuring highly concurrent usage and operational reliability.}
\resumeItem{Actively \textbf{exploring and upskilling in Google Cloud Platform (GCP)} and its suite of ML services to architect scalable AI infrastructures and predictive data models.}
\resumeItem{Developing and optimizing RESTful architectures with \textbf{Node.js, Express.js, TypeScript}, and ensuring seamless state integration in React.js applications.}
\resumeItemListEnd

\resumeSubheading
{Cognitivo}{Jun 2024 -- Aug 2025}
{Full Stack Developer}{Hybrid}
\resumeItemListStart

\resumeItem{Integrated \textbf{AI-powered conversational features (OpenAI GPT-based)} directly into applications, providing intelligent user assistance, automating responses, and increasing user retention.}
\resumeItem{Architected and optimized end-to-end \textbf{RESTful and GraphQL APIs} using \textbf{Node.js and PostgreSQL/MongoDB}, improving query efficiency and supporting a \textbf{50\% increase in concurrent user traffic}.}
\resumeItem{Built \textbf{Web Push Notifications} using Service Workers and VAPID keys to implement real-time event-driven alert systems.}
\resumeItem{Integrated complex \textbf{third-party platforms} including Monday.com via custom webhooks and automation scripts, accelerating cross-team operational efficiency.}
\resumeItem{Refactored legacy UI components using \textbf{React.js, TypeScript, Material UI, and Tailwind CSS}, drastically improving frontend performance, responsiveness, and web accessibility.}
\resumeItemListEnd

\resumeSubheading
{Singularies Pvt Ltd}{Jan 2023 -- May 2024}
{Software Engineer}{Remote}
\resumeItemListStart
\resumeItem{Designed and implemented robust features for a key product, writing maintainable logic utilizing \textbf{TypeScript, React.js, and Remix frameworks}.}
\resumeItem{Developed scalable backend microservices using \textbf{Go (Golang)} and integrated critical third-party APIs ensuring high reliability and fault tolerance.}
\resumeItem{Created high-performance, reusable UI components with \textbf{Tailwind CSS}, focusing on an inclusive, accessible user experience across all devices.}
\resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart



    \resumeProjectHeading
        {\textbf{Twitter Clone} $|$ \emph{Node.js, Express, MongoDB, JWT}}{\href{https://github.com/yashshuklaaa/Twiteer-clone}{\underline{Source Code}}}
    \resumeItemListStart
        \resumeItem{Developed a robust backend architecture using \textbf{Node.js and Express.js}, providing core functionalities for user authentication, tweet creation, and dynamic timeline management.}
        \resumeItem{Implemented secure authentication flows utilizing \textbf{JSON Web Tokens (JWT)} and password hashing with \textbf{bcryptjs} to protect user data and sessions.}
        \resumeItem{Integrated complex relational features including user associations (follow/unfollow) and interaction systems (likes and comments), ensuring efficient data management in \textbf{MongoDB}.}
        \resumeItem{Designed and rigorously tested a comprehensive \textbf{RESTful API} using \textbf{Postman}, ensuring reliable, well-documented endpoints for seamless frontend integration.}
    \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{AI \& Cloud (Exploring):}{ AI Integrations (LLMs, Prompts, Extraction), Google Cloud Platform (GCP), Vertex AI} \\
     \textbf{Languages:}{ TypeScript, JavaScript, Go, C++, SQL, HTML/CSS} \\
     \textbf{Frontend:}{ React.js, Remix, Tailwind CSS, Material UI, Redux} \\
     \textbf{Backend \& Databases:}{ Node.js, Express.js, MongoDB, PostgreSQL, REST/GraphQL APIs} \\
     \textbf{Tools:}{ Git, Docker, Postman, VS Code}
    }}
\end{itemize}

%-----------ACHIEVEMENTS-----------
\section{Achievements}
\begin{itemize}      
    \resumeItem{Ranked \textbf{1st in College} on \href{https://auth.geeksforgeeks.org/user/yashshuklal20}{\textbf{GeeksforGeeks}}}
    \resumeItem{\textbf{3 Star} Coder on \href{https://leetcode.com/Shukla_Yash/} {\textbf{LeetCode}} (1540 rating, Top 34\%)}  
    \resumeItem{Solved \textbf{1000+ Data Structure and Algorithm Problems} across LeetCode, GFG, and CodeChef} 
    \resumeItem{Maintained an \textbf{831-day longest streak} on \href{https://leetcode.com/Shukla_Yash/}{\textbf{LeetCode}}}   
\end{itemize}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
    \resumeSubheading
        {Rajkiya Engineering College Bijnor}{2020--2024}
        {Bachelor of Technology in Electrical Engineering; CGPA: 7.56/10}{Bijnor, India}
\resumeSubHeadingListEnd

\end{document}
